---
title: "Teaching in Production"
author:
- name: Alison Hill, Ph.D.
  url: https://alison.rbind.io
  affiliation: RStudio
  affiliation_url: https://rstudio.com
date: "`r Sys.Date()`"
description: |
  Day 3 of the RStudio Instructor Training and Certification Program.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Make your teaching more robust & reproducible with R Markdown",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "rstudio-education/teaching-in-production") %>% 
  meta_social(
    title = "Teaching in Production",
    url = "https://rstd.io/tip",
    image = "https://repository-images.githubusercontent.com/288797104/d13f1700-e2cc-11ea-9ed7-0bf3a41af1e4",
    image_alt = "R Markdown hedgehog by Allison Horst",
    og_type = "website",
    twitter_card_type = "summary_large_image"
  )
```

## Welcome  

These are the materials for an invited session for Day 3 of the RStudio Instructor Training and Certification Program, by Dr. Alison Presmanes Hill.

```{r embed-xaringan, echo=FALSE, fig.cap="[Slides](slides/index.html)"}
xaringanExtra::embed_xaringan(url = "slides/index.html", ratio = "16:9")
```
\

## Prework

We assume that you have knit an R Markdown document before, but you don’t need to be an advanced R Markdown user to participate! You'll get the most out of this session if you are familiar with: 

+ the basics of R Markdown^[see <https://rmarkdown.rstudio.com/lesson-1.html> for a refresher],

+ the RStudio Integrated Development Environment (IDE), and

+ GitHub via the RStudio IDE. 




<aside>You won't have to use GitHub for the session, but many of tools we'll use integrate nicely with version control via GitHub. To get started, complete these [installation instructions](https://happygitwithr.com/install-intro.html), then test your connection between GitHub and RStudio following [these steps](https://happygitwithr.com/connect-intro.html).^[We *strongly recommend* that if you are not already a fluent GitHub user you choose [HTTPS over SSH](https://happygitwithr.com/credential-caching.html).]. </aside>

You'll also need to install the following packages:

```{r eval=FALSE, echo=TRUE}
install.packages(c("xaringan", "distill", "palmerpenguins"))
```


\

## Links

+ Link to this website: <https://rstd.io/tip>

+ [Slides](slides/index.html)





## Acknowledgments {.appendix}

This is website made with the [distill package](https://rstudio.github.io/distill/) and a custom theme by Alison Hill & [Desirée De Leon](https://desiree.rbind.io/).
